Technology-based aids for people affected by Autism Spectrum Disorder (ASD)

### 2017-11-16 paper.tex
Advance in first section

%% Glossary
\newacronym{asd}{ASD}{Autism Spectrum Disorder}
\newacronym{va}{VA}{Virtual Agents}

@@

%TODO Avatar-based techniques to improve the performances of the therapy
%TODO Methods to detect the anxiety level
To improve the performances of the sessions, the use of \gls{va} has been introducted.
\gls{va} consist of an Avatar, that can be a robot or a virtual character, a learning software that receive information from the Avatar, elaborate them and adjust the response of the Avatar, and an interface for the therapist to interpretate the results.
In a \gls{va} session, the therapist, with the aids of the learning software, learns the Avatar in order to do an action that the child has to imitate, the child tries to imitate the Avatar learning new way to interact with the society.
Different system has been proposed, we propose here two different solutions, one more general and one more complex and efficient.

\subsection{General AVATAR idea}
\label{sec:avatar_general}
The idea of an Avatar-based therapy session is proposed firstly in \cite{Guerrero-vasquez}. They propose a

>>>>

%% Glossary
\newacronym{asd}{ASD}{Autism Spectrum Disorder}
\newacronym{va}{VA}{Virtual Agents}
\newacronym{dof}{DoF}{Degrees of Freedom}

@@

%TODO Avatar-based techniques to improve the performances of the therapy
%TODO Methods to detect the anxiety level
To improve the performances of the sessions, the use of \gls{va} platforms has been introducted.
A \gls{va} platform consist of an avatar, that can be a robot or a virtual character, a learning software that receive information from the Avatar, elaborate them and adjust the response of the Avatar, and an interface for the therapist to interpretate the results.
In a \gls{va} session, the therapist, with the aids of the learning software, learns the Avatar in order to do an action that the child has to imitate, the child tries to imitate the Avatar learning new way to interact with the society.
Different system has been proposed, we propose here two different solutions, one more general and one more complex and efficient.

\subsection{General AVATAR idea}
\label{sec:avatar_general}

\begin{figure}[h]
\centering

\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{avatar_system.png}
\caption{Scheme of AVATAR system}
\label{fig:avatar_scheme}
\end{minipage}
\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{avatar_tasks.png}
\caption{Structure of AVATAR platform}
\label{fig:avatar_tasks}
\end{minipage}

\end{figure}

The idea of an Avatar-based therapy session is proposed firstly in \cite{Guerrero-vasquez}. They propose a system composed by a \gls{va} and an \textit{expert system} used by the therapist to instruct the \gls{va}. A general scheme of the proposed system is shown in \autoref{fig:avatar_scheme}.

They chose to use a Virtual Agent instead of a robot since, according with the needs, it provides the possibility to customize the tool, while a robot is limitated on its shape and its \gls{dof}.

As can be seen in \autoref{fig:avatar_tasks}, the platform is organized as follow:
\begin{LaTeXdescription}
	\item[Child Interface] It selects the child's favourite Virtual Agent and uses interaction tools as screen, camera, microphone and speakers to interact with the child;
	\item[Expert System] Contains a learning algorithm that promotes interaction between the child and the Virtual Agent, it stores the scenario and features of the Virtual Agent and it monitors progress of the session in order to generate statistical reports that will be used by the therapist;
	\item[Therapist Interface] Allow the therapist to access to the reports generated by the Expert System and gives information about the current therapy, in order to allow the therapist to draw conclusions.
\end{LaTeXdescription}

The key point is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
Since the VA that the child observes on his screen is a disguise of his therapist, combined with artificial intelligence, is actually the therapist who promotes the interaction in combination with the expert system.
